Experience-Biased Symbolic Planning

### 2014-05-13 AAAI_AuthorKit/paper.tex
Added paragraph on parallelizability

@@

\section{Analysis of HSPr}

>>>>

Finally, we remark that the Experience-Biased HSP algorithm is highly parallelizable, even if A* is retricted to expanding nodes sequentially. Recall that the sum, min and max functions are computable in logarithmic time using linearly many processors. With minor adjustments, then, ComputeG($S$) has parallel depth $O(\mathbf{A\log A\log O})$. With $\mathbf{AO}$ processors, the total cost of generating a state is $O(\mathbf{(A\log O + \log V^E)\log A})$. Using even more processors, the cost of \textit{expanding} a state can be reduced to the same by generating its successors in parallel.

@@

\section{Analysis of HSPr (section might be deleted, but please have a look)}
